Response to RC1 of ``When does vapor pressure deficit drive or reduce evapotranspiration?''

### 2018-12-23 doc/paper/hess-revision/review-3.tex
done with responses, all posted

We agree with your comments and will respond with some general views
to open the door for further discussion in this discussion phase. We
look forward to reconciling all reviews with a revised manuscript and
formal response in the final response phase. Also of relevance to this
review is our \href{https://editor.copernicus.org/index.php/hess-2018-553-AC1.pdf?_mdl=msover_md&_jrl=13&_lcm=oc108lcm109w&_acm=get_comm_file&_ms=72556&c=153745&salt=17166479111051651323}{
  response to RC1}, which we will refer to as needed to avoid
repeating content.

@@

\section{Methods/Introduction}
Adding the clarifications you suggest for the methods section will
greatly improve the manuscript, as well as more thorough discussion in
the introduction about what is known about the transpiration response to
VPD. This is also discussed peripherally in our response to
\href{https://editor.copernicus.org/index.php/hess-2018-553-RC2.pdf?_mdl=msover_md&_jrl=13&_lcm=oc108lcm109w&_acm=get_comm_file&_ms=72556&c=153384&salt=74148443849227084}{RC2}.

@@

In our response to RC1 we discussed a few revision approaches
regarding the results, some of them including significant changes,
which should help both with acknowledging g$_1$ and uWUE variability
and streamlining the results. One example (``Option 2'') is to remove
the PFT focus from the first portion of the results (Section 3.1-3.2;
this could also go in Methods as you suggest), and instead focus
generally on how changes in the environment (e.g. wind speed,
temperature) and land surface terms (e.g. g$_1$, uWUE, canopy height)
influence the ET response. Using a more sophisticated representation
of uncertainty we could then present the distribution of
observation-informed ET responses as a function of the model terms
(g$_a$, uWUE, g$_1$, etc.), and finally tie all this to either PFTs or
specific sites with maps of statistics from the distribution of model
parameters and ET response. While this could add a lot of analysis and
content to the paper, we think in the end it could streamline the
results and their interpretation. Basically we would start with the
idealized ET response as a function of parameters (no uncertainty), to
the observed ET response as a function of parameters (with
uncertainty), to how both the parameters and ET response (with
uncertainty) map to specific sites, years and/or PFTs. Thoughts on
this are welcome.

>>>>

We agree with your comments and will respond with some general views
to open the door for further discussion in this discussion phase. We
look forward to reconciling all reviews with a
formal response in the final response phase. Also of relevance to this
review is our \href{https://editor.copernicus.org/index.php/hess-2018-553-AC1.pdf?_mdl=msover_md&_jrl=13&_lcm=oc108lcm109w&_acm=get_comm_file&_ms=72556&c=153745&salt=17166479111051651323}{
  response to RC1}, which we will refer to as needed to avoid
repeating content.

@@

\section{Methods/Introduction}
A more thorough discussion in the introduction about what is known
about the transpiration response to VPD is definitely needed. This is
also discussed peripherally in our response to
\href{https://editor.copernicus.org/index.php/hess-2018-553-AC2.pdf?_mdl=msover_md&_jrl=13&_lcm=oc108lcm109w&_acm=get_comm_file&_ms=72556&c=154058&salt=19427645101542423504}{RC2}. The clarifications you
suggest for the methods section will also improve the manuscript.

@@

In our response to RC1 we discussed a few revision approaches
regarding the results, some of them including significant changes,
which should help both with acknowledging g$_1$ and uWUE variability
and streamlining the results. One example (``Option 2'') is to remove
the PFT focus from the first portion of the results (Section 3.1-3.2;
this could also go in Methods as you suggest), and instead focus
generally on how changes in the environment (e.g. wind speed,
temperature) and land surface terms (e.g. g$_1$, uWUE, canopy height)
influence the ET response. By using a more sophisticated representation
of uncertainty we could then present the distribution of
observation-informed ET responses as a function of the model terms
(g$_a$, uWUE, g$_1$, etc.), and finally tie all this to either PFTs or
specific sites with maps of statistics from the distribution of model
parameters and ET response. While this could add a lot of analysis and
content to the paper, we think in the end it could streamline the
results and their interpretation. Basically we would start with the
idealized ET response as a function of parameters (no uncertainty), to
the observed ET response as a function of parameters (with
uncertainty), to how both the parameters and ET response (with
uncertainty) map to specific sites, years and/or PFTs. Thoughts on
this are welcome.
